Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-22 string_jpam.tex
fixes #12
fixes #10

Compare the above analysis with a taut {\em heavy} string which
adopts, at least locally, a catenary configuration at closest
approach~\cite{nguyen2007}.  Such a configuration is manifestly convex
to the singularity, in contrast to light strings which are concave.

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition would suggest that the black hole feels a force to
the left, and should start accelerating.  However, it is not clear by
what mechanism such a force would be transmitted: the situation is
steady, so no gravitational waves are produced, and the string is
inextensible so stores no energy.  Further work might include analysis
of taut strings near a spinning black hole.

>>>>

Compare the above analysis with a taut {\em heavy} string which
adopts, at least locally, a catenary configuration at closest
approach~\cite{nguyen2007}.  A heavy string is manifestly convex to
the singularity in the sense that $R<0$ if $\phi'=0$, in contrast to
light strings which have $R>0$.

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition, and d'Alembert's principle, would suggest that
the black hole should accelerate to the left.  Note that the strings
are already ``straight'' in sense that they are minimal length; so
altering the tension would not change their path.  However, it is not
clear by what mechanism the required force would be transmitted: the
situation is steady, so no gravitational waves are produced, and the
string is inextensible so stores no energy.  Further work might
include analysis of taut strings near a spinning black hole.
